---
title: "HW5 notebook"
output: html_notebook
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r}
library(rgdal)
library(tmap)
library(tmaptools)
library(sp)
library(osmdata)
library(OpenStreetMap)
locations <- readOGR(dsn="C:/Users/ridhi/OneDrive/Documents/CS-585-DB/Ridhi_Shikha_HW5/mygeodata",layer="hw_five")
location1 <- read_osm(locations)
tm_shape(location1)+tm_raster()+tm_shape(locations)+tm_dots(col = "red",size=2,shape = 16)


```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

```{r}
library(PBSmapping)
library(ggmap)
loca <- importShapefile("C:/Users/ridhi/OneDrive/Documents/CS-585-DB/Ridhi_Shikha_HW5/mygeodata/hw_five.shp") 
dataf<- data.frame(loca)
point<- get_map(location = c(lon=-118.282833,lat=34.021853),zoom=15)
ggmap(point)+geom_point(data=dataf,aes(X,Y),size=5,color="red")
```


